A sensor grid approach for large scale acoustic monitoring

### 2017-06-19 paper/article.tex
fie fixes

\address{felix.gontier@reseau.eseo.fr\\mathieu.lagrange@cnrs.fr}

\begin{abstract}
%% Text of abstract
The advent of low cost acoustic sensors together with the need to better monitor and comprehend the acoustic environment of urban and wilderness areas give rise to the deployment of experimental sensor networks such as the sonyc (wp.nyu.edu/sonyc) and cense (cense.ifsttar.fr) projects.

Together with the estimation of acoustic indicators (LAeq, ...), one important aspect of those networks is their ability to detect the presence of sound sources of interest ( bird calls, sirens, explosion, ...) in order to better assess soundscapes. This detection step can be operated online (on the sensors) or offline (on the data servers).

The former is efficient in terms of data storage as only the detection events are transmitted. Though, it requires the availability of computing resources on the sensors in order to perform the detection step, and the detection is done once and cannot be recomputed.

But, for transmission from the sensors to the storage unit, the data needs to be encoded in an efficient way. Also, as the data is transmitted using the network and stored, one must ensure that the intelligibility of potential speech utterances is lost during the coding process, in order to ensure the privacy of the citizens.

The coding scheme described in this paper has the following features. It is of low bitrate but still allows the computation of most of the standard acoustics indicators with high precision. As far as acoustic event detection is concerned, we report equivalent performance of several state of the art classification schemes from features computed using raw audio data and encoded data. Finally, according to preliminary perceptual evaluation, the proposed coding scheme very strongly degrades the intelligibility, thus ensuring citizen privacy.

In order to promote reproducible research, the coder as well as the experiments needed to generate the figures will be made available to the community.

@@

As such, there is a strong need for the development of the so-called "sensor grid" approach  \cite{lim2005sensor,tham2005sensorgrid} for the monitoring of the acoustic environment, be it from urban, rural or wilderness areas.

The sensor grid approach put the focus on a) a distributed system of data acquisition with a large set of sensors, b) the production and storage of a large dataset, and c) its availability for intensive and open data analysis computation.

requirements

scalability:
power managment:
security and privacy:
data richness:

low consumption computation (processing and transmission) of the sensor node

low bitrate of the transmitted data for efficient transmission and storage

proposed approach

%\begin{figure}[t]
%\includegraphics[width=\columnwidth]{figures/censeCoder}
%\vspace{-0.15in}
%\caption{}
%\label{fig:codingScheme}
%\end{figure}

\section{Background}

@@

A common way to implement third-octave analysis is to first design the highest octave three filters, and use them on progressively time-decimated versions of the input signal \cite{davis1986}. In practice, however, this technique presents multiple issues. \cite{antoni2010} presents an alternative analysis method based on direct frequency weighting. The weights matrix design procedure complies with both ANSI S1.1-1986 and IEC 61260-1:2014 standards. It also respects the partition of unity principle over all frequency bins in the relevant range. Resulting filters for different parameter $l$ values are compared with Couvreur's implementation \cite{couvreur} of the time-domain filtering, as shown in Figure~\ref{fig:freq_filt}. The major difference is that gains at cutoff frequencies are fixed at the optimal -3dB by design.\\

@@

\section{Results}

@@

\ml{pourquoi parler d'overlap ici, alors que le codeur ne doit en utiliser ?}

@@

\begin{figure}[htbp]
	\centering
		\includegraphics[width=\columnwidth]{percint_mel_avg.eps}
	\caption{Results of the perceptual intelligibility test.}
	\label{fig:percint_mel_avg}
\end{figure}

\fg{figures a refaire}
\section{Conclusion}

>>>>

\address{felix.gontier@reseau.eseo.fr \\ mathieu.lagrange@cnrs.fr}

\begin{abstract}
%% Text of abstract

The acoustic environment represents both societal and environmental concerns, in particular for cities that are subjected to a multitude of noise sources and that count de facto numerous exposed people.

In this context, monitoring the acoustic environnment in urban but also rural or wilderness areas is an important matter. Fostering on the recent development of low cost hardware acoustic sensors, we propose to using a sensor grid approach.

audio sensing

audio encoding

@@

The advent of low cost acoustic sensors together with the need to better monitor and comprehend the acoustic environment of urban and wilderness areas give rise to the deployment of experimental sensor networks such as the sonyc (wp.nyu.edu/sonyc) and cense (cense.ifsttar.fr) projects.

To do so, considering the so-called "sensor grid" approach  \cite{lim2005sensor,tham2005sensorgrid} has several advantages. The sensor grid approach put the focus on a) a distributed system of data acquisition with a large set of sensors, b) the production and storage of a large dataset, and c) its availability for intensive and open data analysis computation.

In our application setting, the requirements are the following. First,  the number of sensor nodes shall be extended as needed without having to change the hardware and software architecture, \textit{i.e.} the approach shall be scalable. Second, the nodes shall be energy efficient in order ot ease the deployment of the sensors grid to the desired topology, ideally autonomous. Third, the data transfer used to transmit the data from the sensor to the storage and processing servers shall be designed with care in order to ensure the privacy of the citizen. Lastly, the data stored shall be as rich as possible while retaining a low bitrate for efficient transmission and storage

The data of interest is first acoustic indicators (LAeq, ...) and second the presence of sound sources of interest (bird calls, sirens, explosion, ...). The latter allow us to better assess soundscapes in terms of pleasantness and other perceptual indicators \cite{lavandier2006contribution, aumond2017modeling}. This detection step can respectively be operated online (on the sensors) or offline (on the data servers).

The former is efficient in terms of data storage as only the detection events are transmitted and is thus currently considered in several approaches \cite{defreville2006automatic, mydlarz2017implementation, mydlarz2015design}. Though, it requires the availability of computing resources on the sensors in order to perform the detection step which as of today's efficiency of hardware d not allow them to be autonomous using power sources like decent size solar panels. Furthermore, the detection is done once and cannot be recomputed during posterior analyses.

However, transmitting the raw audio through the network has several disavantages, in terms of required bandwidth, storage capabilities and privacy.Thus, for transmission from the sensors to the storage unit, the data needs to be encoded in an efficient way. Also, as the data is transmitted using the network and stored, one must ensure that the intelligibility of potential speech utterances is lost during the coding process, in order to ensure the privacy of the citizens.

We thus propose in this paper a audio coding scheme specifically tailored for use in a sensor grid which has the following features. It is of low bitrate but still allows the computation of most of the standard acoustics indicators with high precision. As far as acoustic event detection is concerned, we report equivalent performance of several state of the art classification schemes from features computed using raw audio data and encoded data. Finally, according to preliminary perceptual evaluation, the proposed coding scheme very strongly degrades the intelligibility, thus ensuring citizen privacy.

In order to promote reproducible research, the coder as well as the experiments needed to generate the figures will be made available to the community. The remaining of the paper is organized as follows: Section \ref{sec:background} reviews the types of data that needs to be estimated using the transmitted data and Section \ref{sec:coder} describes the proposed encoding schemeSection. the experimental protocol designed to validate the proposed approach is described in Section \ref{sec:protocol} and results are discussed in Section \ref{sec:results}.

\begin{figure}[t]
\includegraphics[width=\columnwidth]{figures/censeCoder}
\vspace{-0.15in}
\caption{Alternative implementations of the sensor grid approach for the monitoring of the acoustic environnment. In A) the raw audio is transmitted, in B) only the detected events, and in C) a compressed spectral representation. Thickness of arrows indicate bandwidth and thickness of boxes indicates the level of computation or storage required.}
\label{fig:codingScheme}
\end{figure}

\section{Background} \label{sec:background}

@@

A common way to implement third-octave analysis is to first design the highest octave three filters, and use them on progressively time-decimated versions of the input signal \cite{davis1986}. In practice, however, this technique presents multiple issues. \cite{antoni2010} presents an alternative analysis method based on direct frequency weighting. The weights matrix design procedure complies with both ANSI S1.1-1986 \cite{citeulike:9580295} and IEC 61260-1:2014 \cite{iec-norm} standards. It also respects the partition of unity principle over all frequency bins in the relevant range. Resulting filters for different parameter $l$ values are compared with Couvreur's implementation \cite{couvreur} of the time-domain filtering, as shown in Figure~\ref{fig:freq_filt}. The major difference is that gains at cutoff frequencies are fixed at the optimal -3dB by design.\\

@@

\section{Results} \label{sec:results}

@@

@@

\begin{figure}[htbp]
	\centering
		\includegraphics[width=\columnwidth]{percint_mel_avg.eps}
	\caption{Results of the perceptual intelligibility test.}
	\label{fig:percint_mel_avg}
\end{figure}
\section{Conclusion}
